An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
add more details to node activeness section

Node activeness is the key concept for defining temporal paths which 
shapes how to traverse an evolving graph. 
Recall an active node $(v,t)$ is a node $v$ at timestamp $t$
that connects to at least another node other that itself.   
It means the entity at that specific timestamp either
receives recommendations or gives recommendations to others (or possibly both).
This implies the entity is ``alive''. Here ``alive'' does not necessary mean physically 
alive. For the case of citation network that we shall discuss later, node activeness more or less means spiritually alive in the sense that the idea or knowledge of the entity is alive.

For adjacency matrices $A^{[s]}$ and $A^{[t]}$, where $s < t$, a nonzero entry
$(i,j)$ of $A^{[s]} A^{[t]}$ indicates a temporal path from $(i,s)$ to $(j,t)$ via
some node $k$ (which is unknown).
In general, a nonzero entry $(i,j)$ of the matrix $A^{[1]}A^{[2]}\cdots A^{[n]}$
indicates a temporal path $p$ that starts at $(i,1)$ and ends at  $(j,n)$.
Notice $p$ must go through at least one edge at each time stamp between $1$ and $n$.
For the evolving graph in Figure \ref{fig:active}, $A^{[1]}A^{[2]}$
is a zero matrix since there is no temporal path from time stamp $t_1$ to $t_2$ that
go through at least one edge at $t_1$. However,
$\langle(1, t_1), (1, t_2), (3,t_2)\rangle$ is a temporal path of Figure \ref{fig:active}.
Notice also if we introduce ones on the diagonal of the matrices $\{A^{[i]}\}$,
each node of the resulting evolving graph will become 
active at all timestamp. Hence matrix-matrix multiplication between consecutive
adjacency matrices should be avoid  for computing temporal paths.

>>>>

Node activeness is the key concept for defining temporal paths which 
shapes how to traverse an evolving graph. 
Recall an active node $(v,t)$ is a node $v$ at timestamp $t$
that connects to at least another node other that itself.   
It means the entity at that specific timestamp either
receives recommendations or gives recommendations to others (or possibly both).
This implies the entity is ``alive''. Here ``alive'' does not necessary mean physically 
alive. For the case of citation network that we shall discuss later, node activeness more or less means spiritually alive in the sense that the idea or knowledge of the entity is alive.
We traverse an evolving graph only on the active nodes.

For adjacency matrices $A^{[s]}$ and $A^{[t]}$, where $s < t$, a nonzero entry
$(i,j)$ of $A^{[s]} A^{[t]}$ indicates a temporal path from $(i,s)$ to $(j,t)$ via
some node $k$ (which is unknown).
In general, a nonzero entry $(i,j)$ of the matrix $A^{[1]}A^{[2]}\cdots A^{[n]}$
indicates a temporal path $p$ that starts at $(i,1)$ and ends at  $(j,n)$.
Notice the fact that $p$ must go through at least one edge at each time stamp between $1$ and $n$.
For the evolving graph in Figure \ref{fig:eg_shortest_path}, $A^{[1]}A^{[2]}$
is a zero matrix since there is no temporal path from time stamp $t_1$ to $t_2$ that
go through at least one edge at $t_1$. However,
$\langle(1, t_1), (1, t_2), (3,t_2)\rangle$ is a temporal path as shown in Figure \ref{fig:active}.
Notice also that if we introduce ones on the diagonal of the matrices $\{A^{[i]}\}$,
each node of the resulting evolving graph will become 
active at all timestamps. 
Hence matrix-matrix multiplication between consecutive
adjacency matrices should be avoid  for computing temporal paths.
